---
title: "Cryptocurrency Dashboard"
author: "Gian Atmaja"
date: "1/17/2021"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    source_code: https://github.com/Gianatmaja/Poisson-Process-Analysis-Cryptocurrency
runtime: shiny
---

```{r setup, include=FALSE}
######################### Libraries ########################### 
library(ggplot2)
library(plotly)
library(dplyr)
library(shiny)
library(flexdashboard)

############################ Data ############################# 
Bitcoin = read.csv('BTC-USD.csv')
Ethereum = read.csv('ETH-USD.csv')
Litecoin = read.csv('LTC-USD.csv')
NEM = read.csv('XEM-USD.csv')
Stellar = read.csv('XLM-USD.csv')
Monero = read.csv('XMR-USD.csv')
XRP = read.csv('XRP-USD.csv')

#######################  Functions ############################
Daily_Changes = function(Data){
  Closing_price = Data$Close
  Pct_change = 100*(Closing_price[2:1827] - Closing_price[1:1826])/Closing_price[1:1826]
  
  return(Pct_change)
}

EDA = function(Change, Gain_input){
  if(Gain_input == "Positive Gains"){
    Num = length(which(Change > 0))
    Den = length(Change)
    Rate = Num/Den
    
    Mean = mean(Change[which(Change > 0)])
    
    Biggest = max(Change)
    Ind = which(Change == Biggest)
    Date_biggest = Dates[Ind+1]
  }else{
    Num = length(which(Change < 0))
    Den = length(Change)
    Rate = Num/Den
    
    Mean = mean(Change[which(Change < 0)])
    
    Biggest = min(Change)
    Ind = which(Change == Biggest)
    Date_biggest = Dates[Ind+1]
  }
  Sol = c(Rate, Mean, Biggest, Date_biggest)
  return(Sol)
}

Count_lambda = function(Data, thres){
  
  Closing_price = Data$Close
  Pct_change = 100*(Closing_price[2:1827] - Closing_price[1:1826])/Closing_price[1:1826]
  
  if (thres < 0){
    sol = length(which(Pct_change <= thres))
  }else{
    sol = length(which(Pct_change >= thres))
  }
  
  return(sol/1826)
}

PP_analysis = function(Key, Gain_input){
  Ind = which(Crypto == Key)
  
  if(Gain_input == "Positive Gains"){
    lambdas = Gain_lambda[Ind,]
  }else{
    lambdas = Loss_lambda[Ind,]
  }
  Range = seq(from = 0, to = 50, by = 1)
  
  Over5 = dpois(Range, 365*lambdas[1])
  Over10 = dpois(Range, 365*lambdas[2])
  Over15 = dpois(Range, 365*lambdas[3])
  Over20 = dpois(Range, 365*lambdas[4])
  
  Sol = data.frame(
    Frequency = Range,
    Over_5_percent = Over5,
    Over_10_percent = Over10,
    Over_15_percent = Over15,
    Over_20_percent = Over20
  )
  
  return(Sol)
}

##############################  Setup  ################################
Dates = Bitcoin$Date
Crypto = c("Bitcoin", "Ethereum", "Litecoin", "NEM", "Stellar", "Monero", "XRP")
N = length(Crypto)
Gain_5 = vector("numeric", N)
Gain_10 = vector("numeric", N)
Gain_15 = vector("numeric", N)
Gain_20 = vector("numeric", N)
Loss_5 = vector("numeric", N)
Loss_10 = vector("numeric", N)
Loss_15 = vector("numeric", N)
Loss_20 = vector("numeric", N)
for (i in 1:N){
  if (i == 1){
    Data = Bitcoin
  }else if (i == 2){
    Data = Ethereum
  }else if (i == 3){
    Data = Litecoin
  }else if (i == 4){
    Data = NEM
  }else if (i == 5){
    Data = Stellar
  }else if (i == 6){
    Data = Monero
  }else{
    Data = XRP
  }
  
  Gain_5[i] = Count_lambda(Data, 5)
  Gain_10[i] = Count_lambda(Data, 10)
  Gain_15[i] = Count_lambda(Data, 15)
  Gain_20[i] = Count_lambda(Data, 20)
  Loss_5[i] = Count_lambda(Data, -5)
  Loss_10[i] = Count_lambda(Data, -10)
  Loss_15[i] = Count_lambda(Data, -15)
  Loss_20[i] = Count_lambda(Data, -20)
}
Gain_lambda = matrix(c(Gain_5, Gain_10, Gain_15, Gain_20), ncol = 4)  
#col 1 = +5%, col 2 = +10%, ...
Loss_lambda = matrix(c(Loss_5, Loss_10, Loss_15, Loss_20), ncol = 4)  
#Same, but - instead of +

```

Sidebar {.sidebar}
=======================================================================
```{r}
selectInput("Asset", label = "Cryptocurrency:",
            choices =c("Bitcoin", "Ethereum", "Litecoin", 
                       "NEM", "Stellar", "Monero", "XRP"), selected = "Bitcoin")

selectInput("Gain", label = "Chosen Gains:",
            choices =c("Positive Gains", "Negative Gains"), selected = "Positive Gains")

```

This dashboard shows an analysis of 7 cryptocurrencies' daily price changes, namely Bitcoin, Ethereum, Litecoin, NEM, Stellar, Monero, XRP. 

Simply choose one of the 7 cryptocurrencies and select which gains to analyse, either positive or negative. 

The smaller boxes in top row show some key figures of the asset, such as the chance of the chosen daily gain (+/-), average size of the positive/ negative daily gains, the largest positive/ negative daily gains recorded, and the date it occurred. 

On the second row, the left plot shows the daily changes (in %) of the asset, while the plot on the right shows the probability distribution function of the frequencies for daily changes of different magnitudes in a year.

Dashboard
=======================================================================

Row
-----------------------------------------------------------------------

### Daily Chance of Chosen Gain

```{r}
Asset_input = reactive({input$Asset})
Gain_input = reactive({input$Gain})
renderGauge({
  Crypto = c("Bitcoin", "Ethereum", "Litecoin", "NEM", "Stellar", "Monero", "XRP")
  Data_Ind = which(Crypto == Asset_input())
  if (Data_Ind == 1){
    Data = Bitcoin
    }else if (Data_Ind == 2){
    Data = Ethereum
  }else if (Data_Ind == 3){
    Data = Litecoin
  }else if (Data_Ind == 4){
    Data = NEM
  }else if (Data_Ind == 5){
    Data = Stellar
  }else if (Data_Ind == 6){
    Data = Monero
  }else{
    Data = XRP
  }

  Asset_Change = Daily_Changes(Data)
  EDA_output = EDA(Asset_Change, Gain_input())

  Chance_gain_loss = round(as.numeric(EDA_output[1])*100)
  if(Gain_input() == "Positive Gains"){
    Success = c(51, 100)
    Warning = c(0, 49)
  }else{
    Success = c(0, 49)
    Warning = c(51, 100)
  }
  gauge(Chance_gain_loss, min = 0, max = 100, symbol = '%', label = "Chance",
        gaugeSectors(success = Success, warning = Warning))
})
```


### Average Value of Chosen Gains

```{r}
library(shinydashboard)
Asset_input = reactive({input$Asset})
Gain_input = reactive({input$Gain})
renderValueBox({
  Crypto = c("Bitcoin", "Ethereum", "Litecoin", "NEM", "Stellar", "Monero", "XRP")
  Data_Ind = which(Crypto == Asset_input())
  if (Data_Ind == 1){
    Data = Bitcoin
    }else if (Data_Ind == 2){
    Data = Ethereum
  }else if (Data_Ind == 3){
    Data = Litecoin
  }else if (Data_Ind == 4){
    Data = NEM
  }else if (Data_Ind == 5){
    Data = Stellar
  }else if (Data_Ind == 6){
    Data = Monero
  }else{
    Data = XRP
  }
  Asset_Change = Daily_Changes(Data)
  EDA_output = EDA(Asset_Change, Gain_input())
  Mean_change = round(as.numeric(EDA_output[2]),2)
  if(Gain_input() == "Positive Gains"){
    Color2 = "green"
    Caption = "Avg Magnitude of Positive Gains (%)"
  }else{
    Color2 = "yellow"
    Caption = "Avg Magnitude of Negative Gains (%)"
  }
  valueBox(Mean_change, Caption, color = Color2)
})
```


### Biggest Movement of Chosen Gain

```{r}
library(shinydashboard)
Asset_input = reactive({input$Asset})
Gain_input = reactive({input$Gain})
renderValueBox({
  Crypto = c("Bitcoin", "Ethereum", "Litecoin", "NEM", "Stellar", "Monero", "XRP")
  Data_Ind = which(Crypto == Asset_input())
  if (Data_Ind == 1){
    Data = Bitcoin
    }else if (Data_Ind == 2){
    Data = Ethereum
  }else if (Data_Ind == 3){
    Data = Litecoin
  }else if (Data_Ind == 4){
    Data = NEM
  }else if (Data_Ind == 5){
    Data = Stellar
  }else if (Data_Ind == 6){
    Data = Monero
  }else{
    Data = XRP
  }
  Asset_Change = Daily_Changes(Data)
  EDA_output = EDA(Asset_Change, Gain_input())
  Biggest_change = round(as.numeric(EDA_output[3]),2)
  if(Gain_input() == "Positive Gains"){
    Caption = "Largest Magnitude of Positive Gains (%)"
  }else{
    Caption = "Largest Magnitude of Negative Gains (%)"
  }
  valueBox(Biggest_change, Caption)
})
```


### Date of Largest Movement

```{r}
library(shinydashboard)
Asset_input = reactive({input$Asset})
Gain_input = reactive({input$Gain})
renderValueBox({
  Crypto = c("Bitcoin", "Ethereum", "Litecoin", "NEM", "Stellar", "Monero", "XRP")
  Data_Ind = which(Crypto == Asset_input())
  if (Data_Ind == 1){
    Data = Bitcoin
    }else if (Data_Ind == 2){
    Data = Ethereum
  }else if (Data_Ind == 3){
    Data = Litecoin
  }else if (Data_Ind == 4){
    Data = NEM
  }else if (Data_Ind == 5){
    Data = Stellar
  }else if (Data_Ind == 6){
    Data = Monero
  }else{
    Data = XRP
  }
  Asset_Change = Daily_Changes(Data)
  EDA_output = EDA(Asset_Change, Gain_input())
  Date_biggest = as.Date(EDA_output[4])
  if(Gain_input() == "Positive Gains"){
    Caption = "Date of Largest Positive Gain (YYYY/MM/DD)"
  }else{
    Caption = "Date of Largest Negative Gain (YYYY/MM/DD)"
  }
  valueBox(Date_biggest, Caption)
})
```


Row
-----------------------------------------------------------------------

### Daily Change in Price (%)

```{r}
Asset_input = reactive({input$Asset})
Gain_input = reactive({input$Gain})
renderPlotly({
  Crypto = c("Bitcoin", "Ethereum", "Litecoin", "NEM", "Stellar", "Monero", "XRP")
  Data_Ind = which(Crypto == Asset_input())
  if (Data_Ind == 1){
    Data = Bitcoin
    }else if (Data_Ind == 2){
    Data = Ethereum
  }else if (Data_Ind == 3){
    Data = Litecoin
  }else if (Data_Ind == 4){
    Data = NEM
  }else if (Data_Ind == 5){
    Data = Stellar
  }else if (Data_Ind == 6){
    Data = Monero
  }else{
    Data = XRP
  }
  Asset_Change = Daily_Changes(Data)
  Change_Table = data.frame(
    Date = as.Date(Dates[2:1827]),
    Percentage_change = Asset_Change
    )
  P1 = ggplot(data = Change_Table) + 
    geom_line(aes(x = Date, y = Percentage_change, group = 1), col = "navy") +
    xlab("\nDate") + ylab("% Change\n") + theme_minimal() + 
    theme(plot.title = element_text(hjust = 0, size = 17 , face = "bold"))
  Plot_1 = ggplotly(P1) 
  Plot_1
})
```


### Probabilities for Shifts of Different Magnitudes (in 1 Year)
```{r}
Asset_input = reactive({input$Asset})
Gain_input = reactive({input$Gain})
renderPlotly({
  PP_output = PP_analysis(Asset_input(), Gain_input())
  if(Gain_input() == "Positive Gains"){
    colors = c("Over 5%" = "gold", "Over 10%" = "olivedrab2", "Over 15%" = "springgreen2", "Over 20%" = "seagreen4")
  }else{
    colors = c("Over 5%" = "mediumpurple2", "Over 10%" = "violetred1", "Over 15%" = "red1", "Over 20%" = "red4")
  }

  P2 = ggplot(data = PP_output) +
    geom_area(aes(x = Frequency, y = Over_5_percent, fill = "Over 5%"), size = 2, alpha = 0.6) + geom_area(aes(x = Frequency, y = Over_10_percent, fill = "Over 10%"), size = 2, alpha = 0.6) + 
    geom_area(aes(x = Frequency, y = Over_15_percent, fill = "Over 15%"), size = 2, alpha = 0.6) +
    geom_area(aes(x = Frequency, y = Over_20_percent, fill = "Over 20%"), size = 2, alpha = 0.6) +
    labs(x = "Frequency", y = "Probability", fill = " ") + scale_fill_manual(values = colors) + theme_minimal() + theme(plot.title = element_text(hjust = 0, size = 17 , face = "bold")) 
  Plot_2 = ggplotly(P2)
  Plot_2
})
```


